\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-29 methodology.tex
more text

>>>>

\PDComment{Based on discussion with Shaz and Cheng, I am trying to do the following: this section will be mostly about the high level overview and how we can model the environment of existing distributed systems and capture all nondeterminism (due to message passing, failures, timers, etc) -- this is not specific to \psharp and thus we could potentially move the \psharp description in the next section and keep this more abstract, but I am not convinced about this. Then the next section is more specifics about \psharp: how the bug-finding runtime works (just overview as its described in our PLDI paper), how the liveness algorithm works, how we handle async/await -- just the generic approach I implemented based on Matt's original work, and maybe some generic discussion about how you can implement extensions of top of \psharp}
